Staged Abstract Interpreters

### 2019-03-18 paper/10_intro.tex
misc

Now to concretely illustrate the idea of Futamura projection, consider that we
have an interpreter @eval@ of some language as following:

@@

\paragraph{Abstraction, Abstraction and Abstraction}
To enable such flexibility between different semantics, we extensively use
abstract type members over multiple abstractions, which can be later instantiated.

>>>>

Now to concretely illustrate the idea of Futamura projection, consider that we
have an operational interpreter @eval@ of some language as following:

@@

\paragraph{Abstraction, Abstraction, and Abstraction}
To enable such flexibility between different semantics, we extensively use
abstract type members over multiple abstractions, which can be later instantiated.
